#第三章  使用最近邻算法进行分类

##一、Nnderstanding classification useing nearest neighors

###1.The kNN algorithm

####1.1 Calculating distance

####1.2 Chossing an appropriate k

####1.3 Preparing data for use with kNN

##二、Diagonosing breast cancer with the kNN algorithm

###1. collecting data

###2. exploring and preparing the data

```{r}
library(ggplot2)
wbcd <- read.csv("resources/wisc_bc_data.csv",stringsAsFactor=FALSE)
str(wbcd)
```

```{r}
wbcd <- wbcd[-1]
str(wbcd)
table(wbcd$diagnosis)
```

```{r}
wbcd$diagnosis <- factor(wbcd$diagnosis,levels=c("B","M"),labels=c("Benign","Malignant"))
round(prop.table(table(wbcd$diagnosis))*100,digits = 1)
```

####2.1 Transformation - normalizing numeric data

To normalize these features, we need to create a normalize() function in R. This function takes a vector x of numeric values, and for each value in x, subtract the minimum value in x and divide by the range of values in x. Finally, the resulting vector is returned. The code for the function is as follows:
```{r}
normalize <- function(x){
  return ((x - min(x))/ (max(x) - min(x)))
}
normalize(c(1,2,3,4,5))
normalize(c(10,20,30,40,50))
wbcd_n <- as.data.frame(lapply(wbcd[2:31],normalize))
summary(wbcd_n$area_mean)
```

####2.2 Data preparation - creating training and test datasets

Using the data extraction methods presented in Chapter 2, Managing and Understanding Data, we will split the wcbd_n data frame into the wbcd_train and wbcd_test data frames:

```{r}
wbcd_train <- wbcd_n[1:469, ]
wbcd_test <- wbcd_n[470:569, ]

```

When we constructed our training and test data, we excluded the target variable, diagnosis. For training the kNN model, we will need to store these class labels in factor vectors, divided to the training and test datasets:

```{r}
wbcd_train_labels <- wbcd[1:469,1]
wbcd_test_labels <- wbcd[470:569,1]
```


###3. training a model on the data

Equipped with our training data and labels vector, we are now ready to classify our unknown records. For the kNN algorithm, the training phase actually involves no model building—the process of training a lazy learner like kNN simply involves storing the input data in a structured format.

```{r}
library(class)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 21)
wbcd_test_pred
```

###4. evaluating model performance

The next step of the process is to evaluate how well the predicted classes in the wbcd_test_pred vector match up with the known values in the wbcd_test_labels vector. To do this, we can use the CrossTable() function in the gmodels
package, which was introduced in Chapter 2, Managing and Understanding Data.

```{r}
library(gmodels)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
```

###5. improving model performance

We will attempt two simle variations on our pervious classifier.First,we will employ an alternative method for rescaling our numeric features.Second,we will try serveral different values for k.

####5.1 Transformation - z-score standardization

```{r}
wbcd_z <- as.data.frame(scale(wbcd[-1]))

summary(wbcd_z$area_mean)
```

```{r}
wbcd_z_train <- wbcd_z[1:469, ]
wbcd_z_test <- wbcd_z[470:569, ]
wbcd_z_train_labels <- wbcd[1:469,1]
wbcd_z_test_labels <- wbcd[470:569,1]
wbcd_z_test_pred <- knn(train = wbcd_z_train,test = wbcd_z_test,cl = wbcd_z_train_labels,k=21)
CrossTable(x = wbcd_z_test_labels,y = wbcd_z_test_pred,prop.chisq=FALSE)
```

####5.2 Testing alternative values of k

```{r}
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 1)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 5)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 11)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 15)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 21)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
wbcd_test_pred <- knn(train = wbcd_train,test = wbcd_test,cl = wbcd_train_labels,k = 27)
CrossTable(x = wbcd_test_labels,y = wbcd_test_pred,prop.chisq=FALSE)
```

