#A Little Data Analysis
Author: EricDoug
Date: 2014-11-19

```{r include=FALSE}
require(mosaic)
require(tigerstats)
```

##The Research Question

Regarding the General Social Survey from the year 2002 (data frame `gss02` form the `tigerstats` package) we are interested in the following Research Question:

>*Is there a relationship,in the U.S. population,between race and gun ownership?*

We will first look at the question descriptively,and then we will address the inferential aspect.

##Descriptive Aspect
The variable in `gss02` that pertain to the research question are **sex** and **owngun**.
Look at the stucture of the data frame:
```{r}
str(gss02)
```
We see at once that

*  **race** is a factor variable with values:
      *African American
      *Hispanic
      *Other
      *White
      
* **owngun** is a factor variable with values
    *"No" (does not own a gun)
    *"Yes" (owns a gun)
    
For convenience,let's think of **race** as the explanatory variable and **owngun** as the reponse.

In order to study the relationship between two these two factor variable,we produce a two-way stable:
```{r echo=FALSE}
RaceGun <- xtabs(~race+owngun,data=gss02)
RaceGun
```

In order to check for a relationship,we need to look at the row percents:

```{r echo=FALSE}
rowPerc(RaceGun)
```




